Outflows from Young Stellar Objects

### 2014-01-07 TALK/TifrTalk.tex
Added movie Slide to pdf
Added more slides

\usepackage{time}       % date and time
\usepackage{graphicx}
\usepackage[T1]{fontenc}    % european characters
%\usepackage{courier}
\usepackage{animate}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{amssymb,amsmath}  % use mathematical symbols
\usepackage{bookman}                  % use palatino as the default font
\setbeamercovered{transparent}
\newcommand{\figpath}{/home/phybva/SiOJets_New/TALK/NEWFIGS}
\newcommand{\spic}[2]{\includegraphics[scale=#1]{#2}}
\newcommand{\myref}[1]{{\small{\color{red}{(#1)}}}}

@@

\section{Outflow dynamics : Propagation}
\begin{frame}{Cooling in Jets}
\end{frame}
\begin{frame}{Molecular Interplay}
\begin{columns}
\begin{column}{0.4\textwidth}
\spic{0.2}{\figpath/pfig6.pdf}
\end{column}
\hfill
\begin{column}{0.6\textwidth}
\spic{0.2}{\figpath/pfig7.pdf}
\end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{Multi-Line survey : Emission I}
Movies Here.
\end{frame}

@@

\begin{frame}{Predictions for ALMA}
\end{frame}

@@

\begin{frame}{Rotation or Wiggles?}
\end{frame}

>>>>

\usepackage{time}       % date and time
\usepackage{graphicx}
\usepackage[T1]{fontenc}    % european characters
%\usepackage{courier}
\usepackage{animate}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{amssymb,amsmath}  % use mathematical symbols
\usepackage{bookman}                  % use palatino as the default font
\setbeamercovered{transparent}
%\newcommand{\figpath}{/home/phybva/SiOJets_New/TALK/NEWFIGS}
\newcommand{\figpath}{./NEWFIGS/}
\newcommand{\spic}[2]{\includegraphics[scale=#1]{#2}}
\newcommand{\myref}[1]{{\small{\color{red}{(#1)}}}}
\newcommand{\movauto}[5]{\animategraphics[width=#1,height=#2,autoplay]{#3}{#4}{0000}{#5}}
\newcommand{\movloop}[5]{\animategraphics[width=#1,height=#2,loop]{#3}{#4}{0000}{#5}}

@@

\section{Outflow dynamics : Propagation}

\begin{frame}{Cooling in Jets}
\begin{columns}
\begin{column}{0.3\textwidth}
\vspace{-3cm}
\begin{block}{Cooling is important}
\begin{itemize}
\item t$_{\rm cool} \sim n_0/\Lambda(T) <$ t$_{\rm dyn}$
  \myref{e.g, Blondin, 1990}\\
\item Cooling rate for a molecular medium with n$_0$ = 10$^{5}$ cm$^{-3}$
\end{itemize}
\end{block}
\end{column}
\begin{column}{0.6\textwidth}
\spic{0.3}{\figpath/pfig1.pdf}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Cooling in Jets}
\begin{block}{Dynamical Effects}
\centering
\begin{itemize}
\item Thinner jets with less pronounced coccoon
\item Enhanced density in the internal knots with instable features.
\item Thermal Instability in bow-shock of the jet. 
\end{itemize}
\end{block}
\centering
\spic{0.23}{\figpath/pfig4.pdf}

\begin{frame}{Molecular Interplay}
\begin{columns}
\begin{column}{0.4\textwidth}
\spic{0.2}{\figpath/pfig6.pdf}
\end{column}
\hfill
\begin{column}{0.6\textwidth}
\spic{0.2}{\figpath/pfig7.pdf}
\end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{Multi-Line survey : Emission I}
\small{
\begin{itemize}
\item Molecular Jet with $\eta$ = 3.0\\
\item Line Intensities with Top Hat Profile. \\
\item Jet is in plane of sky and convolved with a Gaussian beam of 2.5''
\end{itemize}
}
\begin{tabular}{ccc}
\textbf{J = 2-$>$1} & \textbf{J = 5-$>$ 4} & \textbf{J = 8-$>$ 7}\\
\movauto{3.5cm}{5.5cm}{3}{Img21/Img21_}{0010}
&
\movauto{3.5cm}{5.5cm}{3}{Img54/Img54_}{0010}
&
\movauto{3.5cm}{5.5cm}{3}{Img87/Img87_}{0010}

\end{tabular}

@@

\begin{frame}{Predictions for ALMA}
\begin{block}{ALMA Cycle 2}
\textbf{Bands 3, 6, 7}: Assuming a source placed at 400 pc.[Orion - HH 212 \myref{Zinnecker,1998}] 
\end{block}
\begin{center}
\spic{0.21}{\figpath/pfig12.pdf}
\end{center}
\end{frame}

@@

\begin{frame}[t]{Rotation or Wiggles?}
  \begin{center}
  \movloop{8cm}{5cm}{61}{Img_3djet/contourjet1.}{0060}
  \end{center}
\end{frame}
